---
title: "Mini Project 3"
description: |
 Small Simulations
author: Ana Jaramillo
date: September 28, 2024
format: html
execute:
  warning: false
  message: false
---

# Option A: Conducting Permutation Test

Data was sourced from \[Real Estate Valuation\](<https://archive.ics.uci.edu/dataset/477/real+estate+valuation+data+set>) from UC Irvine Machine Learning Repository by I-Cheng Yeh

This dataset shows the historical market of real estate valuation collected from Sindian Dist., New Taipei City, Taiwan. It has many interesting variables to compare–features of homes that may increase or decrease its valuation. In particular, distance from homes to the nearest MRT station interested me, as Taiwan has an extensive public transport system; MRT being one of the most popular.

As such, it wouldn't be a far fetch to believe a home's distance from an MRT station might increase valuation. As such, we might like to test the correlation between these variables to understand how significant MRT distance truly is to Taiwan's real estate market.

**Research Question:** Is there a significant association between distance from the nearest MRT station and house price per unit area in Taiwan?

**Null Hypothesis:** There is no association between the distance to the nearest MRT station and house price per unit area.

**Alternative Hypothesis:** There is an association between the distance to the nearest MRT station and house price per unit area.

```{r}
library(tidyverse)
library(readxl)

# Data
real_estate <- read_excel("C:/Users/anaja/Downloads/Real estate valuation data set.xlsx")
```

Let's start by visualizing. I have started by plotting a graph with the dataset's original values for MRT distance and their associated price per unit area. Clearly, the slope is pretty negative, perhaps showing that the farther a home is from an MRT station, the less expensive the price per unit area.

However, how much of this is due to random chance? Could it be that all these MRT distance data points lined up just right to show a negative relationship?

Lets try to rearrange the MRT distance data randomly to see if we get the same relationship. To do so, we are sampling the existing MRT distances and assigning them randomly to house price per unit area. As we can see, the linear model shows a much more neutral slope.

```{r}
# Linear regression of Normal MRT Distance to House Price per Unit Area
real_estate |>
  ggplot(aes(x = distance_MRT, y = house_price_unit)) +
  geom_point() +
  labs(x = "Distance from MRT (meters)", y = "House Price of Unit Area", y = "House Price of Unit Area",
       title = "MRT Distances to House Price per Unit Area" ) +
  geom_smooth(method = "lm")


# Linear regression of Randomly Sampled MRT Distances to House Price per Unit Area
set.seed(47)
real_estate |>
    mutate(random_MRT = sample(distance_MRT)) |>
    ggplot(aes(x = random_MRT, y = house_price_unit)) +
    geom_point() +
  labs(x = "Distance from MRT (meters)", y = "House Price of Unit Area",
       title = "Randomly Sampled MRT Distances to House Price per Unit Area") +
  geom_smooth(method = "lm")
  
```

But how much can we really trust our eyes? Lets get some numerical data to back up our claim. Here, we calculate the observed slope's coefficient to numerically understand how much of a difference we see in slopes.

```{r}
# Getting the observed slope for original data and plot
observed_model <- lm(house_price_unit ~ distance_MRT, data = real_estate)
observed_slope <- coef(observed_model)[["distance_MRT"]]

observed_slope

# Running Permutation Test with slope for Null Hypothesis
set.seed(47)

permuted_MRT_prices <- function(real_estate) {
  real_estate <- real_estate |>
    mutate(random_MRT = sample(distance_MRT))
  model_random_MRT <- lm(house_price_unit ~ random_MRT, data = real_estate)
  return(coef(model_random_MRT)[["random_MRT"]])
}

permuted_MRT_prices(real_estate)

```

Okay, but that was just ONE instance of reshuffling. Maybe this was all chance! Any good scientist knows we should have multiple trials–like 1000 iterations...

```{r}
# Iterating over multiple random samples of MRT distance
set.seed(47)

n_permutations <- 1000
null_slopes <- map_dbl(1:n_permutations, ~ permuted_MRT_prices(real_estate))

average_sample_slope <- mean(null_slopes)

average_sample_slope

```

So over 1000 permutations, we have an average reshuffled slope of:

```         
2.056867e-05
```

This is compared to our very negative slope of the original dataset:

```         
 -0.007262052
```

In all, it seems that proximity to MRT stations may play a significant role in Taiwan's house valuation. The original dataset's negative relationship is shown to be significantly different from the 1000 iterations of permutations tested with randomized data.

Citation:

Yeh, I. (2018). Real Estate Valuation \[Dataset\]. UCI Machine Learning Repository. <https://doi.org/10.24432/C5J30W.>
