---
title: "Real Estate Simulation"
description: |
 Real Estate Simulations
author: Ana Jaramillo
date: November 8, 2024
format: html
execute:
  warning: false
  message: false
---

Data was sourced from [Real Estate Valuation](https://archive.ics.uci.edu/dataset/477/real+estate+valuation+data+set) from UC Irvine Machine Learning Repository by I-Cheng Yeh.

This dataset provides insights into the historical market of real estate valuation collected from Sindian Dist., New Taipei City, Taiwan. It includes many interesting variables for comparison, such as features of homes and their potential association with valuation. In particular, the distance from homes to the nearest MRT station stood out, as Taiwan’s extensive public transportation system, including its popular MRT, plays a significant role in daily life.

I was interested in examining whether there is a significant association between the distance of homes from the nearest MRT station and house price per unit area. While one might hypothesize that proximity to an MRT station increases valuation, the dataset itself does not provide evidence for causal claims—our analysis focuses solely on the association between these variables.

**Research Question:** Is there a significant association between distance from the nearest MRT station and house price per unit area in Taiwan?

**Null Hypothesis:** There is no association between the distance to the nearest MRT station and house price per unit area.

**Alternative Hypothesis:** There is an association between the distance to the nearest MRT station and house price per unit area.

# Visualizing the Data

```{r}
library(tidyverse)
library(readxl)

# Data
real_estate <- read_excel("C:/Users/anaja/Downloads/Real estate valuation data set.xlsx")
```

To start, I plotted the observed relationship between MRT distance and house price per unit area. The slope of the linear regression model appears negative, suggesting that homes closer to MRT stations tend to have higher prices per unit area. However, this visual pattern could occur by chance. To assess the significance of this relationship, I will conduct a permutation test.

```{r}
# Linear regression of Normal MRT Distance to House Price per Unit Area
real_estate |>
  ggplot(aes(x = distance_MRT, y = house_price_unit)) +
  geom_point() +
  labs(x = "Distance from MRT (meters)", y = "House Price of Unit Area",
       y = "House Price of Unit Area",
       title = "MRT Distances to House Price per Unit Area" ) +
  geom_smooth(method = "lm")


# Linear regression of Randomly Sampled MRT Distances to House Price per Unit Area
set.seed(47)
real_estate |>
    mutate(random_MRT = sample(distance_MRT)) |>
    ggplot(aes(x = random_MRT, y = house_price_unit)) +
    geom_point() +
  labs(x = "Distance from MRT (meters)", y = "House Price of Unit Area",
       title = "Randomly Sampled MRT Distances to House Price per Unit Area") +
  geom_smooth(method = "lm")
  
```

Here, we calculate the observed slope's coefficient to numerically understand how much of a difference we see in slopes.

```{r}
# Getting the observed slope for original data and plot
observed_model <- lm(house_price_unit ~ distance_MRT, data = real_estate)
observed_slope <- coef(observed_model)[["distance_MRT"]]

observed_slope

# Running Permutation Test with slope for Null Hypothesis
set.seed(47)

permuted_MRT_prices <- function(real_estate) {
  real_estate <- real_estate |>
    mutate(random_MRT = sample(distance_MRT))
  model_random_MRT <- lm(house_price_unit ~ random_MRT, data = real_estate)
  return(coef(model_random_MRT)[["random_MRT"]])
}

permuted_MRT_prices(real_estate)

```

# Conducting a Permutation Test

A permutation test reshuffles the MRT distances randomly and calculates a new slope each time. By comparing the observed slope from the original data to the distribution of slopes generated from 1000 random permutations, we can evaluate whether the observed relationship is likely to have arisen by chance.

The observed slope for the original dataset is **-0.0073**, while the average slope from the null distribution of 1000 permutations is approximately **0.00002**, indicating a near-zero association under the null hypothesis. When plotted, the histogram of null slopes clearly shows that the observed slope (red line) lies far outside the null distribution, suggesting that the observed negative slope is statistically significant.

```{r}
# Iterating over multiple random samples of MRT distance
set.seed(47)

n_permutations <- 1000
null_slopes <- map_dbl(1:n_permutations, ~ permuted_MRT_prices(real_estate))

average_sample_slope <- mean(null_slopes)

average_sample_slope


```

So over 1000 iterations, we have an average reshuffled slope of:

```         
2.056867e-05
```

This is compared to our very negative slope of the original dataset:

```         
 -0.007262052
```

Lets create a histogram of the null statistics and see if our observed values fall within the histogram:

```{r}
comparison_slopes <- tibble(null_slopes, observed_slope)

set.seed(47)
perm_stats <-
  map(1:1000, null_slopes, data = comparison_slopes) |>
  list_rbind()

perm_stats |>
  ggplot(aes(x = null_slopes)) +
  geom_histogram() +
  geom_vline(aes(xintercept = observed_slope), color = "red") +
               labs(title = "Histogram of 1000 Slope Permutations", 
                    subtitle = "red line = observed slope (from original data)", x = "Permuted Null Slopes", y = "Count")
```

It seems our observed slope (red line) is not near the slopes calculated in 1000 iterations. That's to say, there is likely no way that our observed data would happen by chance--even if we were to run this simulation 1000 times.

# Statistical Testing

To complement the permutation test, I conducted a linear regression analysis. I reported the p-value associated with the slope of the regression line (not the intercept). The p-value for the slope (4.639825e-56) is essentially **0 (\<\< 0.05)**, allowing us to confidently reject the null hypothesis. This result aligns with the permutation test, further supporting the conclusion that there is a statistically significant association between house prices per unit area and the distance to the nearest MRT station.

```{r}
library(broom)
t_test <- lm(house_price_unit ~ distance_MRT, data = real_estate) |>
  tidy()

t_test$p.value
```

# Results and Implications

The analyses show strong evidence of a negative association between MRT proximity and house price per unit area in Taiwan. While this study does not establish causality, the results suggest that proximity to MRT stations may be an important factor associated with real estate valuation. Future studies could extend this analysis to other regions or include additional variables to better understand the dynamics of Taiwan’s real estate market.

Citation:

Yeh, I. (2018). Real Estate Valuation \[Dataset\]. UCI Machine Learning Repository. <https://doi.org/10.24432/C5J30W.>
